A linearization procedure for constrained multibody systems

### 2012-03-30 PetersonGedeHubbard2012.tex
Improved intro.

\begin{abstract}
  We present a systematic procedure for linearizing equations of motion
  governing constrained multibody systems which have been derived with Kane's
  method.  The procedure avoids differential algebraic equations and yields
  linear relationships between time derivatives of generalized
  coordinates/speeds (both independent and dependent) and independent
  generalized coordinates/speeds and exogenous inputs.  These minimal
  linearized equations effectively embed the constraints within them, and
  enable stability analysis and control system design without the need to
  explicitly address the constraints.  We numerically validate the results on a
  well studied model of a bicycle which includes both configuration and
  velocity constraints.
\keywords{symbolic dynamics, control, constrained multibody systems}
\end{abstract}

@@

The goal of the following calculations is to concretely establish the first
order relationships (about an arbitrary equilibrium point) between an arbitrary
choice of independent coordinates and speeds, and the time-derivatives of all
coordinates and speeds (both independent and dependent).  This enables several
common tasks: (1) stability analysis, (2) control system design, (3) control
system design with output feedback based upon quantities that are dependent
(i.e., not state variables), (4) determination of measurement equations for use
in Kalman filter design when measured quantities are at the acceleration level
(i.e., accelerometers).  The formalism presented here is generic enough to
cover most examples of time-varying constrained multibody systems with
arbitrary external inputs and arbitrary specified quantities.  This procedure
has been created for systems whose equations of motion have been derived with
Kane's Method; while this is not a strict requirement, systems
which can be completely described by a set of ODEs is (i.e., no DAEs).

>>>>

\begin{abstract}
  We present a systematic procedure for linearizing equations of motion
  governing constrained multibody systems which have been derived with Kane's
  method.  The procedure avoids differential algebraic equations and yields
  linear relationships between time derivatives of generalized
  coordinates/speeds (both independent and dependent) and independent
  generalized coordinates/speeds and exogenous inputs.  These linear ODE's
  effectively embed the constraints, and enable stability analysis and control
  system design without the need to explicitly address the constraints.  We
  numerically validate the results on a well studied model of a bicycle which
  includes both configuration and velocity constraints.
\keywords{symbolic dynamics, control, constrained multibody systems}
\end{abstract}

@@

The goal of the following calculations is to concretely establish the first
order relationships (about an arbitrary equilibrium point) between an arbitrary
choice of independent coordinates and speeds, and the time-derivatives of all
coordinates and speeds (both independent and dependent).  This enables several
common tasks: (1) stability analysis, (2) control system design, (3) control
system or estimator design which involve dependent quanties (i.e, position
control on a dependent coordinate or measurements at acceleration level).  The
formalism presented here is generic enough to cover most examples of
time-varying constrained multibody systems with arbitrary external inputs and
arbitrary specified quantities.  This procedure has been created for systems
whose equations of motion have been derived with Kane's Method; while this is
not a strict requirement, systems which can be completely described by a set of
ODEs is (i.e., no DAEs).
